Trauma treatment delay

### 2023-10-31 manuscriptlongversion.Rmd
flowchart

We conducted a registry based cohort study using data from the trauma
registry and trauma care quality database at the Karolinska University
Hospital in Solna. The trauma registry includes about 14000 patients
treated between 2012 and 2022. The trauma care quality database is a
subset of the trauma registry and includes about 8000 patients selected
for review between 2013 and 2022. This project will link the two
databases and assess how different patient level factors, such as age,
sex, mechanism of injury, and injury severity, are associated with
delayed treatment using logistic regression.

@@

>>>>

We conducted a registry based cohort study using data from the trauma
registry and trauma care quality database at the Karolinska University
Hospital in Solna. The trauma registry includes about 11864 patients
treated between 2012 and 2022. The trauma care quality database is a
subset of the trauma registry and includes about 8000 patients selected
for review between 2013 and 2022. This project will link the two
databases and assess how different patient level factors, such as age,
sex, mechanism of injury, and injury severity, are associated with
delayed treatment using logistic regression.

@@

## Results

Out of the 11864 patients treated at KS between 2012 and 2022, 1835 were
included in the study. The patient characteristics were as follows in
Table 1.

```{r}
  factors.data %>%
    tbl_summary(  # Create summary statistics for different groups
      by = OFI_delay,
      label = list(
        Age = "Age (years)",
        Gender = "Gender",
        Total_GCS = "GCS"
      ),
      statistic = list(all_continuous() ~ "{mean} ± {sd}"),
      digits = list(all_continuous() ~ c(2, 2))
    ) %>%
    add_p()  # Add p-values

```
